\documentclass[margin, 10pt] {report}

\usepackage{url}
\begin{document}

\noindent
Dear Sir/Madam, \\

\noindent
I am Computer Science graduate at KTH, defending my thesis in October 2014. My area of expertise lies mainly in machine learning and high performance computing. I am well-versed in processing and mining big-data using machine learning techniques, and I have demonstrated it both in research (mining terabytes of DNA data) and in industry (mining terabytes of US demographic data to find best caller/agent match in call center application, and  mining gigabytes of financial data for forecasting stock trends).

\noindent
I am social, outgoing, and love to collaborate in a multi-disciplinary teams. I believe that great ideas are created and developed by team-effort and therefore being socially outgoing is a great plus to accelerate the creativity process in any field of endeavor.

\noindent
I am especially interested to be part of Volvo's data analytics team not only because this is exactly what I have been doing until now both at the industry and in a research capacity, but also because Volve is striving for greener solutions necessary for a greener environment which is my passion too. Having being part of the team that designed and implemented data mining systems which are actively used by Fortune 500 companies, I think I can capitalize on my previous industry and consulting experience to be part of Volvo family in big success stories.

\noindent
I am very optimistic about listening from you, and to explain how I may be a good addition to the data analystics team. I am currently residing at Stockholm, but I have no problems with relocation. I may be reached anytime via email \url{ikramu@kth.se} or via phone +46-73-9366175. \\

\noindent
Best regards, 

\noindent
Ikram Ullah
\end{document}
